---
title: "Chapter 16 - Evaluative uses"
author: "Bodo Winter"
date: "8/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is the analysis for Chapter 16, which explores the evaluative uses of sensory words. In addition, the comparison between different sense operationalizations from Chapter 15 will be continued.

We begin by loading in the data and libraries.

```{r packages_data, message = FALSE}
## Libraries:

library(png)		# for plotting sensory modality images
library(car)
library(MASS)
library(tidyverse)
library(stringr)

## Load data:

lyn <- read_csv('../processed-data/lyn_cluster.csv')
war <- read_csv('../raw-data/valence_warriner_2013.csv')
snef <- read_delim('../raw-data/snefjella_kuperman_context_valence.csv',
                   delim = ' ')
SUBTL <- read_csv('../raw-data/frequency_SUBTLEX_POS.csv')

## Load plotting functions:

source('../functions/boxplot_fnc.R')
```

This time, we will use the image data (from freepix.com). So let's load in images and specify the color values.

```{r image_setup}
## Load in images:

s1 <- readPNG('../figures/sight.png')
s2 <- readPNG('../figures/touch.png')
s3 <- readPNG('../figures/sound.png')
s4 <- readPNG('../figures/taste.png')
s5 <- readPNG('../figures/smell.png')

## Define vector of names:

sense_names <- str_c('s', 1:5)

## Define colors:

mycols <- c('#f37058', '#f79038', '#efbe1b',
            '#425fac', '#30b77d')
```

First, we need to compute the absolute valence measure for the Warriner et al. (2013) and the Snefjella and Kuperman (2016) data.

```{r valence_compute}
## Compute absval for Warriner et al. (2013):

war <- mutate(war,
              Val_c = V.Mean.Sum - mean(V.Mean.Sum),
              Val_z = Val_c / sd(Val_c),
              AbsVal = abs(Val_z))

## Compute absval for Snefjella & Kuperman (2016):

snef <- mutate(snef,
               ContextVal_c = Context_Valence - mean(Context_Valence),
               ContextVal_z = ContextVal_c / sd(ContextVal_c),
               ContextAbsVal = abs(ContextVal_z))
```

Merge everything:

```{r merge}
## Warriner et al. (2013):
lyn <- left_join(lyn,
                 select(war, Word, Val_z, AbsVal),
                 by = c('Word' = 'Word'))

## Snefjella & Kuperman (2016)

lyn <- left_join(lyn,
	select(snef, Word, ContextVal_c:ContextAbsVal),
	by = c('Word' = 'Word'))
```

Get descriptive stats for the measures:

```{r measure_descriptive}
mean(lyn$Val_z, na.rm = TRUE)
range(lyn$Val_z, na.rm = TRUE)
mean(lyn$AbsVal, na.rm = TRUE)
range(lyn$AbsVal, na.rm = TRUE)
mean(lyn$ContextVal_z, na.rm = TRUE)
range(lyn$ContextVal_z, na.rm = TRUE)
mean(lyn$ContextAbsVal, na.rm = TRUE)
range(lyn$ContextAbsVal, na.rm = TRUE)
```

Check overlap between the different datasets:

```{r check_overlap}
## Warriner et al. (2013):

sum(!is.na(lyn$AbsVal))
sum(!is.na(lyn$AbsVal)) / nrow(lyn)

## Snefjella & Kuperman (2016):

sum(!is.na(lyn$ContextAbsVal))
sum(!is.na(lyn$ContextAbsVal)) / nrow(lyn)
```

Check correlation between valence and context valence.

```{r val_contextval}
# Valence:

cor.test(lyn$ContextVal_z,
         lyn$Val_z, use = 'complete.obs')
```

Biggest mismatch between context and non-context valence:

```{r val_contextval_residuals}
# Get rid of NAs:

lyn_no_NA <- filter(lyn,
                    complete.cases(ContextVal_z, Val_z))

# Fit model:

valcomp_mdl <- lm(ContextVal_z ~ Val_z, data = lyn_no_NA)

# Extract residuals:

lyn_no_NA$Res <- residuals(valcomp_mdl)

# Check:

arrange(lyn_no_NA, desc(Res)) %>%
  select(Word, Val_z, ContextVal_z, Res)
arrange(lyn_no_NA, Res) %>%
  select(Word, Val_z, ContextVal_z, Res)
filter(lyn_no_NA,
       Res < 0.1,
       Res > -0.1) %>% 
  select(Word, Val_z, ContextVal_z, Res)
```

Compute log-transformed frequencies from SUBTLEX (necessary for ordering clusters).

```{r SUBTLEX_logs}
SUBTL <- SUBTL %>%
  rename(Freq = FREQcount) %>%
  mutate(LogFreq = log10(Freq + 1))

## Merge this into the main data frame:

lyn <- left_join(lyn,
                 select(SUBTL, Word, Freq, LogFreq),
                 by = c('Word' = 'Word'))
```

## Setup for plotting

First, we get ordered clusters, in order of sense, then frequency:

```{r clust_order}
class_order <- lyn %>% group_by(Class, Image) %>%
  summarize(LogFreq = mean(LogFreq, na.rm = TRUE)) %>%
	arrange(Image, desc(LogFreq)) %>% pull(Class)

image_order <- lyn %>% group_by(Class, Image) %>%
	summarize(LogFreq = mean(LogFreq, na.rm = TRUE)) %>%
	arrange(Image, desc(LogFreq)) %>% pull(Image)

color_order <- mycols[as.numeric(as.factor(image_order))]
```

Then we put in the labels into the main data frame:

```{r add_label_df}
lyn <- mutate(lyn,
              Clust = factor(Class, levels = class_order))
```

Next, the plotting parameters:

```{r plot_pars}
x_fac <- 0.15
x_fac_img <- 0.3
y_fac_img <- 0.036
```

## All boxplots

This will plot all boxplots:

```{r all_boxplots}
boxplot_fnc(lyn, 'AbsVal',
            ylims = c(0, 3),
            ylab = 'Absolute Valence',
            which_x = 0,
            y_axis = seq(0, 5, 1),
            hlty = 1)
boxplot_fnc(lyn, 'ContextAbsVal',
            ylims = c(0, 2.5),
            ylab = 'Absolute Valence (Contexts)',
            which_x = 0,
            y_axis = seq(0, 2.5, 0.5),
            hlty = 1)
boxplot_fnc(lyn, 'ContextVal_z',
            ylims = c(-2.5, 2.5),
            ylab = 'Valence (Contexts)',
            which_x = 0,
            y_axis = seq(-2.5, 2.5, 0.5),
            hlty = 2)
```

## Absolute valence (Warriner et al., 2013)

For each of the emotional valence measures, we now compare a model with the clusters, with the dominant modality classifications, and with the continuous measures.

```{r abs_val}
## Clusters:

summary(absval.class <- lm(AbsVal ~ Class, lyn))
anova(absval.class)

## Dominant modality:

summary(absval.mod <- lm(AbsVal ~ DominantModality, lyn))
anova(absval.mod)

## Descriptive means:

lyn %>% group_by(DominantModality) %>% 
  summarize(AbsValM = mean(AbsVal, na.rm = TRUE),
            AbsValSD = sd(AbsVal, na.rm = TRUE)) %>% 
  mutate(AbsValM = round(AbsValM, 1),
         AbsValSD = round(AbsValSD, 1))

## Continuous model:

summary(absval.cont <- lm(AbsVal ~ VisualStrengthMean +
                            GustatoryStrengthMean +
                            OlfactoryStrengthMean +
                            HapticStrengthMean +
                            AuditoryStrengthMean, lyn))
summary(absval.cont.null <- lm(AbsVal ~ 1, lyn))
anova(absval.cont.null, absval.cont, test = 'F')
anova(absval.cont)

## Check collinearity:

vif(absval.cont)

## BICs:

BIC(absval.class);BIC(absval.mod);BIC(absval.cont)
```

## Context absolute valence (Snefjella & Kuperman, 2016):

Next, we repeat these analyses for the context-based valence from Snefjella & Kuperman (2016):

```{r context_absval}
## Cluster model:

summary(conabs.class <- lm(ContextAbsVal ~ Class, lyn))
anova(conabs.class)

## Dominant modality model:

summary(conabs.mod <- lm(ContextAbsVal ~ DominantModality, lyn))
anova(conabs.mod)

## Descriptive means:

lyn %>% group_by(DominantModality) %>% 
  summarize(ContextAbsValM = mean(ContextAbsVal,
                                 na.rm = TRUE),
            ContextAbsValSD = sd(ContextAbsVal,
                                   na.rm = TRUE)) %>% 
  mutate(ContextAbsValM = round(ContextAbsValM, 1),
         ContextAbsValSD = round(ContextAbsValSD, 1))

## Continuous model:

summary(conabs.cont <- lm(ContextAbsVal ~ VisualStrengthMean +
                            GustatoryStrengthMean +
                            OlfactoryStrengthMean +
                            HapticStrengthMean +
                            AuditoryStrengthMean, lyn))
summary(conabs.cont.null <- lm(ContextAbsVal ~ 1, lyn))
summary(conabs.cont)$r.squared
anova(conabs.cont.null, conabs.cont, test = 'Chisq')
anova(conabs.cont)

## Collinearity:

vif(conabs.cont)

## BIC:

BIC(conabs.class);BIC(conabs.mod);BIC(conabs.cont)
```

## Valence (positve/negative) (Warriner et al., 2013)

The absolute valence measure looks at "emotionality" regardless of whether it's positive or negative.

```{r pos_neg_war}
## Cluster model:

summary(val.class <- lm(Val_z ~ Class, lyn))
anova(val.class)

## Dominant modality model:

summary(val.mod <- lm(Val_z ~ DominantModality, lyn))
anova(val.mod)

## Descriptive means:

lyn %>% group_by(DominantModality) %>% 
  summarize(Val_zM = mean(Val_z, na.rm = TRUE),
            Val_zSD = sd(Val_z, na.rm = TRUE)) %>% 
  mutate(Val_zM = round(Val_zM, 1),
         Val_zSD = round(Val_zSD, 1))

## Average valence per modality:

aggregate(Val_z ~ DominantModality, lyn, mean)

## Continuous model:

summary(val.cont <- lm(Val_z ~ VisualStrengthMean +
                          GustatoryStrengthMean +
                          OlfactoryStrengthMean +
                          HapticStrengthMean +
                          AuditoryStrengthMean, lyn))

val.cont.null <- lm(Val_z ~ 1, lyn)
anova(val.cont.null, val.cont, test = 'F')
anova(val.cont)

## Check collinearity:

vif(val.cont)

## BICs:

BIC(val.class);BIC(val.mod);BIC(val.cont)
```

## Context valence (positve/negative) (Snefjella & Kuperman, 2016):

The absolute valence measure looks at "emotionality" regardless of whether it's positive or negative.

```{r pos_neg_snef}
## Cluster model:

summary(conval.class <- lm(ContextVal_z ~ Class, lyn))
anova(conval.class)

## Dominant modality model:

summary(conval.mod <- lm(ContextVal_z ~ DominantModality, lyn))
anova(conval.mod)

## Descriptive means:

lyn %>% group_by(DominantModality) %>% 
  summarize(ContextVal_zM = mean(ContextVal_z, na.rm = TRUE),
            ContextVal_zSD = sd(ContextVal_z, na.rm = TRUE)) %>% 
  mutate(ContextVal_zM = round(ContextVal_zM, 1),
         ContextVal_zSD = round(ContextVal_zSD, 1))

## Average valence per modality:

aggregate(Val_z ~ DominantModality, lyn, mean)

## Continuous model:

summary(conval.cont <- lm(ContextVal_z ~ VisualStrengthMean +
                          GustatoryStrengthMean +
                          OlfactoryStrengthMean +
                          HapticStrengthMean +
                          AuditoryStrengthMean, lyn))

conval.cont.null <- lm(ContextVal_z ~ 1, lyn)
anova(conval.cont.null, conval.cont, test = 'F')
anova(conval.cont)

## Check collinearity:

vif(conval.cont)

## BICs:

BIC(conval.class);BIC(conval.mod);BIC(conval.cont)
```


## Taste versus smell post-hoc comparison

Taste is predicted to be more positive than smell.

```{r taste_smell_posthoc}
chemsense <- filter(lyn,
                    DominantModality %in% c('Gustatory', 'Olfactory'))

wilcox.test(Val_z ~ DominantModality,
            data = chemsense, paired = FALSE)
t.test(Val_z ~ DominantModality,
       data = chemsense, paired = FALSE)

wilcox.test(ContextVal_z ~ DominantModality,
            data = chemsense, paired = FALSE)
t.test(ContextVal_z ~ DominantModality,
       data = chemsense, paired = FALSE)
```

## Absolute valence: chemical senses vs. rest

Let's test the difference in absolute valence between the chemical senses and the rest. First, let's create a column to identify these senses.

```{r assign_chems}
chem <- c('Gustatory', 'Olfactory')
lyn <- mutate(lyn,
              ChemVsRest = ifelse(DominantModality %in% chem,
                                  'chem', 'rest'))
```

Next, let's create models for this:

```{r chem_vs_rest_models}
# Create models:

absval.chem <- lm(AbsVal ~ ChemVsRest, lyn)
absval.context.chem <- lm(ContextAbsVal ~ ChemVsRest, lyn)

# Check r-squared:

summary(absval.chem)$r.squared
summary(absval.context.chem)$r.squared

# Check BIC:

BIC(absval.chem)
BIC(absval.context.chem)
```


## Assumptions

Check plots of residuals against fitted values for all models:

```{r assumptions, fig.width = 10, fig.height = 4}
# Absolute valence, cluster:

par(mfrow = c(1, 2))
plot(fitted(absval.class), residuals(absval.class))
qqnorm(residuals(absval.class)); qqline(residuals(absval.class))

# Absolute valence, categorical:

par(mfrow = c(1, 2))
plot(fitted(absval.mod), residuals(absval.mod))
qqnorm(residuals(absval.mod)); qqline(residuals(absval.mod))

# Absolute valence, continuous:

par(mfrow = c(1, 2))
plot(fitted(absval.cont), residuals(absval.cont))
qqnorm(residuals(absval.cont)); qqline(residuals(absval.cont))

# Context absolute valence, cluster:

par(mfrow = c(1, 2))
plot(fitted(conabs.class), residuals(conabs.class))
qqnorm(residuals(conabs.class)); qqline(residuals(conabs.class))

# Context absolute valence, categorical:

par(mfrow = c(1, 2))
plot(fitted(conabs.mod), residuals(conabs.mod))
qqnorm(residuals(conabs.mod)); qqline(residuals(conabs.mod))

# Context absolute valence, continuous:

par(mfrow = c(1, 2))
plot(fitted(conabs.cont), residuals(conabs.cont))
qqnorm(residuals(conabs.cont)); qqline(residuals(conabs.cont))

# Valence, cluster:

par(mfrow = c(1, 2))
plot(fitted(val.class), residuals(val.class))
qqnorm(residuals(val.class)); qqline(residuals(val.class))

# Valence, categorical:

par(mfrow = c(1, 2))
plot(fitted(val.mod), residuals(val.mod))
qqnorm(residuals(val.mod)); qqline(residuals(val.mod))

# Valence, continuous:

par(mfrow = c(1, 2))
plot(fitted(val.cont), residuals(val.cont))
qqnorm(residuals(val.cont)); qqline(residuals(val.cont))

# Context valence, cluster:

par(mfrow = c(1, 2))
plot(fitted(conval.class), residuals(conval.class))
qqnorm(residuals(conval.class)); qqline(residuals(conval.class))

# Context valence, categorical:

par(mfrow = c(1, 2))
plot(fitted(conval.mod), residuals(conval.mod))
qqnorm(residuals(conval.mod)); qqline(residuals(conval.mod))

# Context valence, continuous:

par(mfrow = c(1, 2))
plot(fitted(conval.cont), residuals(conval.cont))
qqnorm(residuals(conval.cont)); qqline(residuals(conval.cont))

```


This completes the analyses presented in Chapter 16.